Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2020-09-07 journal paper/content/sec-intro.tex
Suppressed a sentence.

\xhdr{Significance.}
Our results have a dual purpose: shed light on real-world implications of some typical scenarios, and investigate the space of models for describing the real world. As an example for the latter, the \HardMax model with simultaneous entry is arguably the most natural model to study \emph{a priori}. However, our results elucidate the need for more refined models that allow for ``free exploration" (\eg via random agents or early entry).

>>>>

\xhdr{Significance.}
Our results have a dual purpose: shed light on real-world implications of some typical scenarios, and investigate the space of models for describing the real world. As an example for the latter: while the \HardMax model with simultaneous entry is arguably the most natural model to study \emph{a priori}, our results elucidate the need for more refined models with ``free exploration" (\eg via random agents or early entry). \asedit{On a technical level, we connect a literature on regret-minimizing bandits in computer science and that on competition in economics.}
